Untrusted B2B Collaboration using the Blockchain

### 2018-07-19 paper/paper.tex
Shrink images a bit
Use monospace font for listings

@@

\subsection{System overview}
\begin{figure}
	\centering
	\includegraphics[width=100mm]{fig/system_diagram.eps}
	\caption{An architecture diagram showing the interactions within the system.} 			
	\label{fig:system_diagram}
\end{figure}

@@

\subsection{Per company setup}
\begin{figure}
	\centering
	\includegraphics[width=70mm]{fig/initialization.eps}
	\caption{A sequence diagram describing the initialization process for an organization.} 
	\label{fig:initialization}
\end{figure}

@@

Given this interface, there are multiple possible implementation approaches for access contracts.
As it was our main focus to develop a running prototype, and not to provide an optimized, production-ready system, we decided on a simple mapping-based implementation:
\begin{lstlisting}[
  caption=Mappings in our access contract implementation,
  language=Solidity,
  basicstyle=\small
]
pragma solidity ^0.4.23;

>>>>

\lstset{basicstyle=\small\ttfamily}

@@

\subsection{System overview}
\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{fig/system_diagram.eps}
	\caption{An architecture diagram showing the interactions within the system.} 			
	\label{fig:system_diagram}
\end{figure}

@@

\subsection{Per company setup}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/initialization.eps}
	\caption{A sequence diagram describing the initialization process for an organization.} 
	\label{fig:initialization}
\end{figure}

@@

Given this interface, there are multiple possible implementation approaches for access contracts.
As it was our main focus to develop a running prototype, and not to provide an optimized, production-ready system, we decided on a simple mapping-based implementation:
\begin{lstlisting}[
  caption=Mappings in our access contract implementation,
  language=Solidity
]
pragma solidity ^0.4.23;
